---
title: "jmartin6_OriginalHomeworkCode_01"
author: "Jess Martin"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
(MODULE 04)
## R Challenge 1

#First, create a vector of 1, word character strings comprising the first line of the novel Ulysses, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”

#Then, extract every third element of this vector.
```{r Challenge 1}
u<- c("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.")
u
require(stringr)
u <- str_split_1(u, " ")
u[seq(from = 1, to = 22, by = 3)]
```
## R Challenge 2

#Given the matrix, m, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable x

#Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x

#Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x

```{r Challenge 2}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
x <- m[4, 5]
x
```
```{r Challenge 2, CONTINUED}
x <- c(m[, 2], m[, 3], m[, 6])
x
x <- c(m[6, ], m[8, ])
x
x <- c(m[2, ], m[6, 2], m[, 9])
x
```
## R Challenge 3

#Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series)

#Given this matrix, what would the following return?

#a[1, 1, 1, 2]

#a[2, 3, 2, ]

#a[1:5, 1:5, 3, 3]

```{r Challenge 3}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a
```
```{r Challenge 3, CONTINUED}
a[1, 1, 1, 2]
```
```{r Challenge 3, CONTINUED 2}
a[2, 3, 2,]
```
```{r Challenge 3, CONTINUED 3}
a[1:5, 1:5, 3, 3]
```
## R Challenge 4
#Create a list representing this (simplified) primate taxonomy:

#Primates
#Haplorhini
#Anthropoidea
#Platyrrhini
#Cebidae
#Atelidae
#Pitheciidae
#Catarrhini
#Cercopithecidae
#Hylobatidae
#Hominidae
#Tarsioidea
#Tarsiidae
#Strepsirhini
#Lorisoidea
#Lorisidae
#Galagidae
#Lemuroidea
#Cheirogaleidae
#Lepilemuridae
#Indriidae
#Lemuridae
#Daubentoniidae

```{r Challenge 4}
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea <- c("Catarrhini", "Platyrrhini")
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Tarsioidea <- c("Tarsiidae")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini
primates <- list(Haplorhini, Strepsirhini)
names(primates) <- list("Haplorhini", "Strepsirhini")
primates
```
## R Challenge 4, Version 2
```{r Challenge 4, Version 2}
  Primates = list(
    Haplorhini = list(
      Anthropoidea = list(
        Platyrrhini = list(
          Cebidae = NULL,
          Atelidae = NULL,
          Pitheciidae = NULL
        ),
        Catarrhini = list(
          Cercopithecidae = NULL,
          Hylobatidae = NULL,
          Hominidae = NULL
        )
      ),
      Tarsioidea = list(
        Tarsiidae = NULL
      )
    ),
    Strepsirhini = list(
      Lorisoidea = list(
        Lorisidae = NULL,
        Galagidae = NULL
      ),
      Lemuroidea = list(
        Cheirogaleidae = NULL,
        Lepilemuridae = NULL,
        Indriidae = NULL,
        Lemuridae = NULL,
        Daubentoniidae = NULL
      )
    )
  )
print(Primates)
```
## R Challenge 5
#Store the following numbers as a 5 x 3 matrix, called “m3”: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2. Be sure to fill the matrix ROW-WISE.

#Then, do the following:

#Coerce the matrix to a data frame.

#As a data frame, coerce the second column to be logical-valued

#As a data frame, coerce the third column to be factor-valued

#When you are done, use the str() command to show the data type for each variable in your dataframe.
  
```{r Challenge 5}
v1 <- matrix(data = c(3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow =  5, ncol = 3)
m3 <- rbind(v1)
m3
df <- data.frame(m3)
df
df[, 2] <- as.logical(df[,2])
df
df[, 3] <- as.factor(df[, 3])
df
str(df)
```
