---
title: "**jmartin6_FinalHomeworkCode_01**"
author: "**Jess Martin**"
date: "**09/20/2023**"
output: 
  prettydoc::html_pretty:
    theme: "hpstr"
    toc: yes
---

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# My Experience with Homework #1

**Three things that I found difficult about this assignment:**

1. After doing the peer commentary, I wanted to make prettification changes in my YAML. Yet, I struggled to load the prettydoc package. Restarting my computer did the trick.
2. I initially had doubts about my success in challenge #4 due to the unusual output. I attempted another version, which yielded the same results. Subsequently, I confirmed with my peers that my approach was indeed correct.
3. I struggled to extract every third element of the vector for challenge 1. Until, Nicole showed me that you need to load the stringr package directly into the Rmd file.

**Three things that I found useful about this assignment:**

1. I learned how to not include a warning message in my knitted Rmd file.
2. I learned how to use bullet points (circle/empty).
3. I learned how to restrict my array output to only a certain number of lines. Much easier to read this way.

**Two things that I liked from my peers comments:**

1. I LOVED the use of prettydoc in Brooke's Rmd!
1. I LOVED the use of a graphic in Bhavya's Rmd!

**One thing I think could have used improvement from my peers comments:**

1. Nothing significant to note, only very minor edits were needed.


# Peer Commentary from Brooke and Bhavya

* In Challenge 1, when loading the stringr function gives a warning, you can make it so that the warning doesn't show up in your html output by referencing the prettification cheat sheets. Done! I supressed this warning message in my knitted Rmd file using: ```{r message=FALSE, warning=FALSE}.

* If you don't want the #s in your final output, you do not need to include them when typing between the chunks. Done! This was a force of habit. I think the removal of the #'s looks significantly better. 

* In challenge 2, the output of your code gives a string of elements. If you want the output to stay in matrix format, you can code it differently. Done! I like the look of both versions.

* In challenge 3, the array is really long in the output. To make it more readable, you could restrict the output to only show a certain number of lines. Done! I used the str() function to complete this. Although, there may be a more efficient/ clear way of doing it.

* In challenge 4, it is cool that you used two different methods! Thank you!

* Also don't forget to make prettification changes in your YAML and body :) Done, definitely looks better now!

<span style="font-size:16pt;">**(AN/BI588: Homework 1: Push It!)**</span> 

<span style="font-size:16pt;">**(MODULE 04)**</span> 

# <span style="font-size:12pt;">**(R Challenge 1)**</span>

Directions:

* First, create a vector of 1, word character strings comprising the first line of the novel Ulysses, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”

* Then, extract every third element of this vector.

```{R Challenge 1}
```{r message=FALSE, warning=FALSE}
u<- c("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.")
u
require(stringr)
u <- str_split_1(u, " ")
u[seq(from = 1, to = 22, by = 3)]
```

# <span style="font-size:12pt;">**(R Challenge 2)**</span>

Directions:

* Given the matrix, m, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable x

* Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x

* Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x

```{R Challenge 2}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
x <- m[4, 5]
x
```

```{r Challenge 2, CONTINUED}
x <- m[,c(2,3,6)]
x
x <- m[c(6,8), ]
x
x <- m[2,2]: m[6,9]
x
```

# <span style="font-size:12pt;">**(R Challenge 3)**</span>

Directions:

* Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series)

* Given this matrix, what would the following return?

  + a[1, 1, 1, 2]

  + a[2, 3, 2, ]

  + a[1:5, 1:5, 3, 3]

```{R Challenge 3}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
str(a)
a

```
```{r Challenge 3, CONTINUED}
a[1, 1, 1, 2]
```
```{r Challenge 3, CONTINUED 2}
a[2, 3, 2,]
```
```{r Challenge 3, CONTINUED 3}
a[1:5, 1:5, 3, 3]
```

# <span style="font-size:12pt;">**(R Challenge 4)**</span>

Directions:

* Create a list representing this (simplified) primate taxonomy:

* Primates
  + Haplorhini
    * Anthropoidea
      + Platyrrhini
        * Cebidae
        * Atelidae
        * Pitheciidae
      + Catarrhini
        * Cercopithecidae
        * Hylobatidae
        * Hominidae
    * Tarsioidea
      + Tarsiidae
  + Strepsirhini
    * Lorisoidea
      + Lorisidae
      + Galagidae
    * Lemuroidea
      + Cheirogaleidae
      + Lepilemuridae
      + Indriidae
      + Lemuridae
      + Daubentoniidae


```{R Challenge 4}
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea <- c("Catarrhini", "Platyrrhini")
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Tarsioidea <- c("Tarsiidae")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini
primates <- list(Haplorhini, Strepsirhini)
names(primates) <- list("Haplorhini", "Strepsirhini")
primates
```

<span style="font-size:12pt;">**(R Challenge 4, Version 2)**</span>

```{R Challenge 4, Version 2}
  Primates = list(
    Haplorhini = list(
      Anthropoidea = list(
        Platyrrhini = list(
          Cebidae = NULL,
          Atelidae = NULL,
          Pitheciidae = NULL
        ),
        Catarrhini = list(
          Cercopithecidae = NULL,
          Hylobatidae = NULL,
          Hominidae = NULL
        )
      ),
      Tarsioidea = list(
        Tarsiidae = NULL
      )
    ),
    Strepsirhini = list(
      Lorisoidea = list(
        Lorisidae = NULL,
        Galagidae = NULL
      ),
      Lemuroidea = list(
        Cheirogaleidae = NULL,
        Lepilemuridae = NULL,
        Indriidae = NULL,
        Lemuridae = NULL,
        Daubentoniidae = NULL
      )
    )
  )
print(Primates)
```

# <span style="font-size:12pt;">**(R Challenge 5)**</span>

Directions:

* Store the following numbers as a 5 x 3 matrix, called “m3”: 3, 0, 1 ,23, 1, 2, 33,    1, 1, 42, 0, 1, 41, 0, 2. Be sure to fill the matrix ROW-WISE.

* Then, do the following:

* Coerce the matrix to a data frame.

* As a data frame, coerce the second column to be logical-valued

* As a data frame, coerce the third column to be factor-valued

* When you are done, use the str() command to show the data type for each variable in   your dataframe.
  
```{R Challenge 5}
v1 <- matrix(data = c(3, 0, 1, 23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow =  5, ncol = 3)
m3 <- rbind(v1)
m3
df <- data.frame(m3)
df
df[, 2] <- as.logical(df[,2])
df
df[, 3] <- as.factor(df[, 3])
df
str(df)
```
